%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry
    {AWS Cloud \& DevEx Engineer} % Job title
    {DPG Media (Freelance)} % Organization
    {Antwerp, Belgium} % Location
    {Nov. 2024 - ...} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintain Backstage (developer platform) AWS infrastructure with CDK Typescript}
        \item {Create scaffolders for  organization in CDK (TS), CloudFormation (SAM) and Terraform}
        \item {Maintain centralized tooling like Artifactory, Jetbrains License Server, Opsgenie, ...}
        \item {Create automated offboarding process for tooling using tooling specific APIs and AWS Step Functions}
        \item {Migrate Public GitHub organizations to GitHub Enterprise}       
        \item {Write GitHub actions and migrate to self-hosted runners on AWS CodeBuild}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AWS Cloud \& Governance Engineer (4/5 until 12/2023 (from then on, 5/5))} % Job title
    {DPG Media (Freelance)} % Organization
    {Antwerp, Belgium} % Location
    {Nov. 2021 - Nov. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {IaC in AWS (CloudFormation (StackSets) and Terraform)}
        \item {Organizational setups in AWS (300+ AWS accounts)}
        \item {Use wide variety of AWS Services in big environment (50+ services)}
        \item {AWS Governance using Lambda (Python), AWS Config, SSM and Step Functions}
        \item {Python development for custom AWS solutions}       
        \item {Very diverse tasks related to AWS networking, AMIs, CI/CD, SSO, containers ...}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Lead (1/5 days until 12/2023)} % Job title
    {Lucidus (Freelance)} % Organization
    {Herentals, Belgium} % Location
    {Nov. 2021 - Dec. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Support in cloud and DevOps setups + EKS PoC for Runtime Fabric}
        \item {Serverless projects in Azure using APIM and Azure Functions}
        \item {Help defining strategies}
        \item {Mentor young graduates}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Operations Engineer} % Job title
    {UnifiedPost Group} % Organization
    {Antwerp, Belgium} % Location
    {Mar. 2021 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working in team in a PCI-DSS compliant environment}
        \item {Monitoring with Suricata and Wazuh}
        \item {Write Terraform for AWS infrastructure}
        \item {Use combination of Packer and Puppet to create AMIs}
        \item {Update Ansible and Ansible Galaxy configurations}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cloud \& DevOps Engineer} % Job title
    {Evolane NV} % Organization
    {Edegem, Belgium} % Location
    {Sept. 2015 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working as a consultant for Evolane NV}
        \item {Self-study and Docker training during my first weeks}
        \item {Organize meetups in the evening for colleagues to talk about new technologies}
        \item {Presenting about Jenkins, Kubernetes deployment strategies, AWS}
        \item {Supervising interns}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cloud \& DevOps Engineer} % Job title
    {Mazda Motor Logistics Europe} % Organization
    {Willebroek, Belgium} % Location
    {Sept. 2017 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Put new and existing AWS resources in CloudFormation or SAM}
        \item {Use wide variety of AWS Services (+30 services)}
        \item {Bash and Python (boto3) scripting (Creating custom git release flow)}
        \item {Draw/develop architectural setups in AWS}
        \item {Maintain and update Jira workflows + Jira/Confluence management}
        \item {Manage and maintain Jenkins + Jenkinsfiles + implement shared library}
        \item {Setup and management of EKS (Kubernetes) cluster + writing Helm Charts}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {Sodexo} % Organization
    {Brussels, Belgium} % Location
    {Jan. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed new deployment strategy in PowerShell}
        \item {SVN to Git migrations of existing repositories}
        \item {Maintain + upgrade CI/CD server TeamCity}
        \item {AWS related challenges with Elastic Beanstalk, S3 and CloudFormation}
        \item {Daily development support}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cloud \& DevOps Engineer} % Job title
    {DBM MyShopi} % Organization
    {Diegem, Belgium} % Location
    {Jan. 2016 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Creating Dockerfiles for applications}
        \item {Build fully persistent Dockerized CI/CD environment with Jenkins and Nexus}
        \item {Build OpenShift Origin environment with Ansible on EC2 instances in AWS}
        \item {Creating pods, services, deployments in OpenShift}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Intern} % Job title
    {ScanTrust} % Organization
    {Shanghai, China} % Location
    {Mar. 2015 - May. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Setup CI/CD environment using Jenkins, Ubuntu and AWS EC2}
        \item {Configure freestyle Jenkins jobs to build, test and deploy Android, Python and Angular applications}
        \item {Create Python hosting environment using Django, Nginx, Gunicorn and Supervisor}        
        \item {First experiences with Npm, Bower, BitBucket, PhantomJs, S3, Sqlite and PostgreSQL}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}